---
title: "Replicating tables 2 and 3 (and table 5D in appendix)"
date: "June 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
### Library
library(sf)
library(ggplot2)
library(tmap)
library(RColorBrewer)
library(dplyr)
library(tidyr)
library(stargazer)
library(stringr)
library(vtable)
library(haven)
library(ggplot2)
library(expss)
library(gridExtra)
library(ggrepel)

```


```{r include=FALSE}

  #Load data
  setwd("../../Extracted Files/Data")
  d.rep <- read_dta("FinalDatasetForReplication.dta")
  d.mil <- read_dta("MilitaryBasesByYear.dta")
  d.vic <- read_dta("VictimsByYear.dta")
  d.lb <- read_dta("LB_Analysis.dta")
  
  #Arrange by province and comuna
  d.rep <- d.rep %>% arrange(IDProv, comuna)
  d.rep <- d.rep %>% select(IDProv, comuna, MainSample, DMilitaryPresence, everything())

```

```{r include=FALSE}

  #Library
  library("fixest")

  #Main variables (as in Dofile of tables)
    # share_allende70 share_alessandri70 Turnout70 
    # share_up71_local mayor_up71 share_up73_congress lnDistStgo 
    # lnDistRegCapital landlocked Pop70_pthousands Houses_pc SocialOrg_pop70 
    # churches_pop70 sh_educ_12more densidad_1970 sh_rural_70 sh_econactivepop_70 
    # sh_women_70 TV ari_1973 index1b" 
  
    #	Controls  
    C <- c("share_allende70", "share_alessandri70", "lnDistStgo", "lnDistRegCapital", "Pop70_pthousands", "sh_rural_70")

    # Weights   
    #W <-  Pop70
    
    #Table 2
      #STATA code: reghdfe shVictims_70 	DMilitaryPresence $C [aw=$W], absorb(IDProv) vce(robust)
     
    #Column 1
      tb2.1 <- feols(shVictims_70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero", weights = ~Pop70)
      #Get same results. Works.

    #Table D5 Robustness checks
    tb2.1.full <- feols(shVictims_70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero", weights = ~Pop70)
      #Get same results. Works.
      #NOTES: 47 observations removed because of 0-weight.
            #These are the counties which do not have province
            #57 observations removed because of NA values (LHS: 53, RHS: 27, Fixed-effects: 52, Weights: 6).
            #We have 53 obs with NA in shVictims_70. The N showed in the table is not the real one.
    
    #Remove weights
      tb2.1.nw <- feols(shVictims_70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero")
        #Continues to be significant
      
   tb2.1.full.nw <- feols(shVictims_70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero")
        #Becomes insignificant (without weights and full population)
    
    #Table 3
      #STATA code: reghdfe Share_reg70_w2 		DMilitaryPresence 	$C [aw=$W], absorb(IDProv) vce(robust)
      
   #Column 1
    tb3.1 <- feols(Share_reg70_w2 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero", weights = ~Pop70)
        #Replicates well
    
    #Column 4 and 3
    tb3.4 <- feols(VoteShareNo_pop70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero", weights = ~Pop70)
        #Replicates well
    tb3.3 <- feols(VoteShareNo ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero", weights = ~Pop70)

    #Table D5, Column 2
   tb3.1.full <- feols(Share_reg70_w2 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero", weights = ~Pop70)
            #Replicates well
            #Note: I get this 
    #NOTES: 47 observations removed because of 0-weight.
            #These are the counties which do not have province
            #57 observations removed because of NA values (LHS: 53, RHS: 27, Fixed-effects: 52, Weights: 6).
    #But in the paper it says its run on all 289. This, as before, is not correct.
   
    #Table D5, Column 3
    tb3.3.full <- feols(VoteShareNo ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero", weights = ~Pop70)
    tb3.4.full <- feols(VoteShareNo_pop70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero", weights = ~Pop70)

    #I am able to replicate this. But this doesnt use the same variable as in the main regression. Its weighted by 1988.
    #Does not do robustness check for column 4. 

   #Explore weights
   table(d.rep$IDProv, d.rep$Pop70, useNA="always")
   
   #Remove weights
   tb3.1.nw <- feols(Share_reg70_w2 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero")
   tb3.4.nw <- feols(VoteShareNo_pop70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero")
    tb3.3.nw <- feols(VoteShareNo ~ DMilitaryPresence + .[C] | IDProv, data = d.rep[d.rep$MainSample==1,], "hetero")
   tb3.1.full.nw <- feols(Share_reg70_w2 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero")
  tb3.3.full.nw <- feols(VoteShareNo ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero")
  tb3.4.full.nw <- feols(VoteShareNo_pop70 ~ DMilitaryPresence + .[C] | IDProv, data = d.rep, "hetero")
   
```

# Replicating effect of military base on repression (Table 2)
  - DV: shVictims_70	(Victims / 10,000 inh. in 1970 census)
  - IV: DMilitaryPresence (Indicator military presence)
  
The first always corresponds to the results in the main text (which are run without the "outliers" and NA
) the second table always correspond to the Table D5 in the robustness checks (and includes all the sample).

```{r echo=FALSE}
print(tb2.1, type = "table")
print(tb2.1.full, type = "table")

```
These replicate well.

## Same regressions removing the 1970 weights

```{r echo=FALSE}
print(tb2.1.nw, type="table")
print(tb2.1.full.nw, type="table")

```
Once we use the full sample and we remove the 1970 weights we loose significance on military presence on repression.

The paper justifies using weights in the following way: "Because our main outcomes of interest, voter registration and support for “No” in the 1988 plebiscite, correspond to individual behaviors, we weight our estimates by population in 1970. This way we ensure that we give equal importance to all voters, irrespective of the size of the county in which they reside".

However, I am not fully grasping this because: their variables are already a share based on the 1970 population. Victims / 10,000 inh. in 1970 census, share of support for NO (Voter registration ( / pop. 1970)), or the share of registration (Share_reg70_w2). So… this is not an individual behaviour anymore. This is an aggregate share of an individual behaviour.

# Replicating effect of military base on voter registration (Table 3)
  - DV: Share_reg70_w2	(Voter registration ( / pop. 1970))
  - IV: DMilitaryPresence (Indicator military presence)
  
```{r echo=FALSE}
print(tb3.1, type="table")
print(tb3.1.full, type="table")
```
These replicate well.

## Same regressions removing the 1970 weights

```{r echo=FALSE}
print(tb3.1.nw, type="table")
print(tb3.1.full.nw, type="table")
```
These continue to be significant and the effect increases.

# Replicating effect of military base on No vote share (Table 3)
  - DV: VoteShareNo_pop70	("NO" vote share (/ pop. 1970))
  - IV: DMilitaryPresence (Indicator military presence)
  
Personally, I find it very weird to calculate the share based on the population of 1970. Surely the population has changed in 18 years. More so if these are areas of high repression, were one could worry that people migrate selectively out of these areas. This is a wider concern: these areas might be comparable in 1970 but if repression did happen so much, the population might have moved endogenously.

```{r echo=FALSE}
print(tb3.4, type="table")
print(tb3.4.full, type="table")

```
These replicate well Table 3 column 4. This is not included in Table 5D. But if we run this in the full sample (second table) it continues to be significant.

## Removing weights

```{r}
print(tb3.4.nw, type="table")
print(tb3.4.full.nw, type="table")

```
Both remain significant without weights.

# Replicating effect of military base on No vote share (Table 3)
  - DV: VoteShareNo ("NO" vote share (/ votes 1988))
  - IV: DMilitaryPresence (Indicator military presence)

Note we are now changing the DV variable to a share computed as NO/votes 1988.

```{r echo=FALSE}
print(tb3.3, type="table")
print(tb3.3.full, type="table")

```
These results replicate well.

## Remove weights
```{r echo=FALSE}
print(tb3.3.nw, type="table")
print(tb3.3.full.nw, type="table")
```
When we calculate the share of NO as a proportion of the votes in 1988 and remove the weights of 1970 we get no significant results on the proportion of vote for no.

# Zoom into weights

```{r}
  table(d.rep[d.rep$Pop70==0,]$IDProv, useNA="always")
```
We have 53 obs without weights. 52 are counties in the "NA" province and 1 in province "23". 
So these nerver enter the regressions. This only bites when they use the full sample of 289.

# Zoom into how this 0 population affects other variables
```{r}
table(d.rep[d.rep$Pop70==0,]$VoteShareNo_pop70, useNA="always")
```
The variable NO vote share is not computed for these 53 obs when is divided by pop 70. This of course happens fot victims and registration share as they are all calculated out of pop 70.

But, these observations do have data for share of NO when calculated out of 1988 votes.
```{r}
table(d.rep[d.rep$Pop70==0,]$VoteShareNo, useNA="always")
```

This to me speaks to population shifting in these 18 years.